Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-08 draft.tex
tiny by o

\subsection{The large $N$ limit of the center ${\frak Z}_n(\UU_n {\frak gl}_N)$ and cyclic cohomology}

@@

By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebras models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) $, 
$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ and $\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ 
equipped with the evaluations maps are given by $\ev_{\mathbf{f}}$, $\ev_{\mathbf{g}}$ and $\ev_{\mathbf{g}\circ \mathbf{f}}$. We are thus left 
to prove that the same  diagram as~\eqref{eq:comdiagforcentralizercomput}, where we replace the objects and maps by their factorization analogue and $\Upsilon$
by $(-\star-)$, is commutative in factorization algebras.

@@

\section{Higher calculus {\it \`a la} Kontsevich and Tamarkin-Tsygan}
\label{sec: TT}

@@

>>>>

\subsection{The large $N$ limit of the center ${\frak Z}_n(\UU_n \frak{gl}_N)$ and cyclic cohomology}

@@

By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebra models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) $, 
$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ and $\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ 
equipped with the evaluations maps are given by $\ev_{\mathbf{f}}$, $\ev_{\mathbf{g}}$ and $\ev_{\mathbf{g}\circ \mathbf{f}}$. We are thus left 
to prove that the same  diagram as~\eqref{eq:comdiagforcentralizercomput}, where we replace the objects and maps by their factorization analogue and $\Upsilon$
by $(-\star-)$, is commutative in factorization algebras.

@@

\section{Higher calculus {\it \`a la} Kontsevich-Soibelman}
\label{sec: TT}

@@

\owen{Mention lots of prior work, e.g., Greg et al, Ayala-Francis, Geoffroy Horel, and so on}
